Detecting Hate Speech with GPT-3

### 2022-02-24 outputs/documents/paper.Rmd
Updates according to R&R comments

Even though large NLP models do not have a real understanding of language, the vocabularies and the construction patterns of harmful languages can be thought of as known to them. We show that this knowledge can be used to identify abusive language and even hate speech. In particular we consider 120 different extracts that have been categorized as 'racist', 'sexist', or 'neither' in the single-category settings and 240 different extracts in the mixed-category settings. We ask GPT-3 to classify these based on zero-, one-, and few-shot learning, with and without instruction. We find that the model performs best with few-shot learning when an instruction is included. In that setting the model can accurately classify around 78 per cent of the extracts. If language models can be used to identify abusive language, then not only is there potential for them to counter the production of abusive language by humans, but they could also potentially self-police.

@@

@@

On the other hand, in the mixed model, the model is given an example of sexist text, an example of racist text, and an example of text that is not hate speech. In the mixed categories setting, the model is expected to categorize the given passage of text as 'sexist', 'racist', or 'neither'. There are ten sets of examples; each set of examples is used for the model to classify 60 racist comments, 60 sexist comments, and 120 comments that are in neither category This results in 2,400 responses in total. The ten sets of examples are available in Table \@ref(tab:appendixa) in the Appendix. An example of this is:

@@

zero_shot_summary <- tibble(Category = c(rep("Racism", 4), rep("Sexism", 4), rep("Overall", 4)), 
                                   Metric = rep(c("Accuracy", "Precision", "Recall", "F1"), 3), 
                                   Percent = c(zero_racism_all, zero_sexism_all, zero_hate_all))

zero_shot_summary %>%
  select(!Category) %>%
  knitr::kable(caption="Performance of zero-shot learning in hate speech classification",
               col.names=c("", "Percent"),
               booktabs=TRUE) %>%
  kableExtra::pack_rows(index = c("Racism"=4, "Sexism"=4, "Overall"=4))
```

@@

one_shot_summary <- tibble(Category = c(rep("Racism", 4), rep("Sexism", 4), rep("Overall", 4)), 
                                   Metric = rep(c("Accuracy", "Precision", "Recall", "F1"), 3), 
                                   Percent = c(one_racism_all, one_sexism_all, one_hate_all))

one_shot_summary %>%
  select(!Category) %>%
  knitr::kable(caption="Performance of one-shot learning in hate speech classification",
               col.names=c("", "Percent"),
               booktabs=TRUE) %>%
  kableExtra::pack_rows(index = c("Racism"=4, "Sexism"=4, "Overall"=4))
```

@@

few_shot_summary <- tibble(Category = c(rep("Racism", 4), rep("Sexism", 4), rep("Overall", 4)), 
                                   Metric = rep(c("Accuracy", "Precision", "Recall", "F1"), 3), 
                                   Percent = c(few_racism_all, few_sexism_all, few_hate_all))

few_shot_summary %>%
  select(!Category) %>%
  knitr::kable(caption="Performance of single-category few-shot learning in hate speech classification",
               col.names=c("", "Percent"),
               booktabs=TRUE) %>%
  kableExtra::pack_rows(index = c("Racism"=4, "Sexism"=4, "Overall"=4))
```

@@

```{r fewshotmixed}
few_shot_mixed_result <-
  read.csv(here::here("outputs/data/few_shot_fixed_examples_results.csv"))

few_shot_mixed_result <-
  few_shot_mixed_result %>%
  filter(temperature == 0) %>%
  select(category, label, answer, example_set) %>%
  mutate(example_set = example_set + 1) %>%
  mutate(result = ifelse(trimws(label) == trimws(answer), "Match", "Mismatch")) %>%
  mutate(
    label = case_when(
      label == "racist" ~ "Racist",
      label == "sexist" ~ "Sexist",
      label == "neither" ~ "Neither"
    )
  ) %>%
  group_by(example_set, result) %>% #, label) %>%
  summarise(result_cnt = n(), .groups = "drop") %>%
  ungroup() %>%
  group_by(example_set) %>%
  mutate(Percent = result_cnt / sum(result_cnt) * 100,
         Percent = round(Percent)) %>%
  rename(Result = result,
         "Example Set" = example_set,
         Count = result_cnt)

knitr::kable(
  few_shot_mixed_result,
  caption = "Classification of statements with mixed-category few-shot learning",
  booktabs = TRUE,
  linesep = "",
  align = 'lllr'
)
```

@@

```{r fewshotmixedinstruct}
few_shot_instruction_result <-
  read.csv(here::here(
    "outputs/data/few_shot_fixed_examples_instruction_results.csv"
  ))

few_shot_instruction_result <-
  few_shot_instruction_result %>%
  filter(temperature == 0) %>%
  select(category, label, answer, example_set) %>%
  mutate(example_set = example_set + 1) %>%
  mutate(result = ifelse(trimws(label) == trimws(answer), "Match", "Mismatch")) %>%
  mutate(
    label = case_when(
      label == "racist" ~ "Racist",
      label == "sexist" ~ "Sexist",
      label == "neither" ~ "Neither"
    )
  ) %>%
  group_by(example_set, result) %>%
  summarise(result_cnt = n(), .groups = "drop") %>%
  ungroup() %>%
  group_by(example_set) %>%
  mutate(Percent = result_cnt / sum(result_cnt) * 100,
         Percent = round(Percent)) %>%

  rename(Result = result,
         "Example Set" = example_set,
         Count = result_cnt)

knitr::kable(
  few_shot_instruction_result,
  caption = "Classification of statements with mixed-category few-shot learning, with instruction",
  booktabs = TRUE,
  linesep = "",
  align = 'lllr'
)

# few_shot_instruction_result %>%
#   group_by(Result) %>%
#   summarise(n = sum(Count)) %>%
#   mutate(Percent = n / sum(n) * 100,
#          Percent = round(Percent))
```

>>>>

Even though large NLP models do not have a real understanding of language, the vocabularies and the construction patterns of harmful languages can be thought of as known to them. We show that this knowledge can be used to identify abusive language and even hate speech. In particular we consider 120 different extracts that have been categorized as 'racist', 'sexist', or 'neither' in the single-category settings and 243 different extracts in the mixed-category settings. We ask GPT-3 to classify these based on zero-, one-, and few-shot learning, with and without instruction. We find that the model performs best with few-shot learning when an instruction is included. In that setting the model can accurately classify around 78 per cent of the extracts. If language models can be used to identify abusive language, then not only is there potential for them to counter the production of abusive language by humans, but they could also potentially self-police.

@@

For the purposes of one-shot and single-category few-shot learning, the dataset was split in half such that 30 racist comments, 30 sexist comments, and 60 neutral comments were used as inputs and the remainder were used as examples. This division was kept consistent for zero-shot learning to allow for the same set of 120 comments to be classified by all three approaches. With the introduction of 10 static example sets for multi-category few-shot learning, 240 comments were classified for each example set.

@@

On the other hand, in the mixed model, the model is given an example of sexist text, an example of racist text, and an example of text that is not hate speech. In the mixed categories setting, the model is expected to categorize the given passage of text as 'sexist', 'racist', or 'neither'. To simplify the classification procedure and allow for comparisons between different example inputs, we created ten sets of examples against which 240 comments were classified each. We elected to use ten example sets to allow for some variation in results while keeping the number of groupings and size of the resulting data set reasonably small.  The example sets each consist of one sexist, one racist, and one 'neither' comment and were created using the comments at indexes one through ten from each dataset. Each set of examples is used for the model to classify 60 racist comments, 60 sexist comments, and 120 comments that are in 'neither' category. The inputted comments were the first _n_ + 1 comments from their respective data sets with the _i_^th comment dropped corresponding to the use of example set _i_. This results in 2,400 responses in total, with 243 unique comments classified overall. The ten sets of examples are available in Table \@ref(tab:appendixa) in Appendix A. An example of this is:

@@

zero_shot_summary <- tibble(Category = c(rep("Racism", 4), rep("Sexism", 4), rep("Overall", 4)), 
                                   Metric = rep(c("Accuracy", "Precision", "Recall", "F1"), 3), 
                                   Percent = c(zero_racism_all, zero_sexism_all, zero_hate_all)) %>%
  pivot_wider(names_from = Metric, values_from = Percent)

zero_shot_summary %>%
  # select(!Category) %>%
  knitr::kable(caption="Performance of zero-shot learning in hate speech classification (percent)",
              # col.names=c(""=1),
               booktabs=TRUE) # %>%
  # kableExtra::pack_rows(index = c("Racism"=4, "Sexism"=4, "Overall"=4))
```

@@

one_shot_summary <- tibble(Category = c(rep("Racism", 4), rep("Sexism", 4), rep("Overall", 4)), 
                                   Metric = rep(c("Accuracy", "Precision", "Recall", "F1"), 3), 
                                   Percent = c(one_racism_all, one_sexism_all, one_hate_all)) %>%
  pivot_wider(names_from = Metric, values_from = Percent)

one_shot_summary %>%
  # select(!Category) %>%
  knitr::kable(caption="Performance of one-shot learning in hate speech classification",
               # col.names=c("", "Percent"),
               booktabs=TRUE) # %>%
  # kableExtra::pack_rows(index = c("Racism"=4, "Sexism"=4, "Overall"=4))
```

@@

few_shot_summary <- tibble(Category = c(rep("Racism", 4), rep("Sexism", 4), rep("Overall", 4)), 
                                   Metric = rep(c("Accuracy", "Precision", "Recall", "F1"), 3), 
                                   Percent = c(few_racism_all, few_sexism_all, few_hate_all)) %>%
  pivot_wider(names_from = Metric, values_from = Percent)

few_shot_summary %>%
  # select(!Category) %>%
  knitr::kable(caption="Performance of single-category few-shot learning in hate speech classification",
               # col.names=c("", "Percent"),
               booktabs=TRUE) # %>%
 # kableExtra::pack_rows(index = c("Racism"=4, "Sexism"=4, "Overall"=4))
```

@@

<!-- ```{r fewshotmixed} -->
<!-- few_shot_mixed_result <- -->
<!--   read.csv(here::here("outputs/data/few_shot_fixed_examples_results.csv")) -->

<!-- few_shot_mixed_result <- -->
<!--   few_shot_mixed_result %>% -->
<!--   filter(temperature == 0) %>% -->
<!--   select(category, label, answer, example_set) %>% -->
<!--   mutate(example_set = example_set + 1) %>% -->
<!--   mutate(result = ifelse(trimws(label) == trimws(answer), "Match", "Mismatch")) %>% -->
<!--   mutate( -->
<!--     label = case_when( -->
<!--       label == "racist" ~ "Racist", -->
<!--       label == "sexist" ~ "Sexist", -->
<!--       label == "neither" ~ "Neither" -->
<!--     ) -->
<!--   ) %>% -->
<!--   group_by(example_set, result) %>% #, label) %>% -->
<!--   summarise(result_cnt = n(), .groups = "drop") %>% -->
<!--   ungroup() %>% -->
<!--   group_by(example_set) %>% -->
<!--   mutate(Percent = result_cnt / sum(result_cnt) * 100, -->
<!--          Percent = round(Percent)) %>% -->
<!--   rename(Result = result, -->
<!--          "Example Set" = example_set, -->
<!--          Count = result_cnt) -->

<!-- knitr::kable( -->
<!--   few_shot_mixed_result, -->
<!--   caption = "Classification of statements with mixed-category few-shot learning", -->
<!--   booktabs = TRUE, -->
<!--   linesep = "", -->
<!--   align = 'lllr' -->
<!-- ) -->
<!-- ``` -->

```{r fewshotmixed-racism}
few_shot_mixed_result <-
  read.csv(here::here("outputs/data/few_shot_fixed_examples_results.csv"))

# Example sets
few_shot_mixed_result_racism <- 
  few_shot_mixed_result %>%
  mutate(example_set = example_set + 1,
         label = case_when(!grepl("racist", label) ~ "not racist", TRUE ~ "racist"),
         answer = case_when(!grepl("racist", answer) ~ "not racist", TRUE ~ "racist")) %>%
  count(example_set, label, answer) %>%
  pivot_wider(names_from = answer, values_from = n) %>%
  mutate(label = case_when(label == "not racist" ~ "Not racist",
                           label == "racist" ~ "Racist")) %>%
  rename("Actual classification" = label, "Not racist" = "not racist", "Racist" = "racist")

# Overall
few_shot_mixed_result_racism_overall <- 
  few_shot_mixed_result %>%
  mutate(example_set = example_set + 1,
         label = case_when(!grepl("racist", label) ~ "not racist", TRUE ~ "racist"),
         answer = case_when(!grepl("racist", answer) ~ "not racist", TRUE ~ "racist")) %>%
  count(label, answer) %>%
  pivot_wider(names_from = answer, values_from = n) %>%
  mutate(label = case_when(label == "not racist" ~ "Not racist",
                           label == "racist" ~ "Racist")) %>%
  rename("Actual classification" = label, "Not racist" = "not racist", "Racist" = "racist")

few_shot_mixed_result_racism <- few_shot_mixed_result_racism[, c("example_set", "Actual classification", "Not racist", "Racist")]
few_shot_mixed_result_racism_overall <- few_shot_mixed_result_racism_overall[, c("Actual classification", "Not racist", "Racist")] %>% mutate(example_set = "All", .before="Actual classification")

table <- few_shot_mixed_result_racism %>% 
  # select(!example_set) %>%
  rbind(few_shot_mixed_result_racism_overall) %>%
  mutate(example_set = case_when(.$`Actual classification` == "Racist" ~ "", TRUE ~ example_set)) %>%
  rename("Example set" = example_set)

knitr::kable(table,
             caption = "Classification of racist statements with mixed-category few-shot learning",
             booktabs = TRUE,
             linesep="") %>%
  kableExtra::add_header_above(c(" " = 2, "GPT-3 classification"=2))  %>%
  kableExtra::row_spec(seq(2, 20, by=2), hline_after = TRUE)
```

```{r fewshotmixed-sexism}
# Example sets
few_shot_mixed_result_sexism <- 
  few_shot_mixed_result %>%
  mutate(example_set = example_set + 1,
         label = case_when(!grepl("sexist", label) ~ "not sexist", TRUE ~ "sexist"),
         answer = case_when(!grepl("sexist", answer) ~ "not sexist", TRUE ~ "sexist")) %>%
  count(example_set, label, answer) %>%
  pivot_wider(names_from = answer, values_from = n) %>%
  mutate(label = case_when(label == "not sexist" ~ "Not sexist",
                           label == "sexist" ~ "Sexist")) %>%
  rename("Actual classification" = label, "Not sexist" = "not sexist", "Sexist" = "sexist")

# Overall
few_shot_mixed_result_sexism_overall <- 
  few_shot_mixed_result %>%
  mutate(example_set = example_set + 1,
         label = case_when(!grepl("sexist", label) ~ "not sexist", TRUE ~ "sexist"),
         answer = case_when(!grepl("sexist", answer) ~ "not sexist", TRUE ~ "sexist")) %>%
  count(label, answer) %>%
  pivot_wider(names_from = answer, values_from = n) %>%
  mutate(label = case_when(label == "not sexist" ~ "Not sexist",
                           label == "sexist" ~ "Sexist")) %>%
  rename("Actual classification" = label, "Not sexist" = "not sexist", "Sexist" = "sexist")

few_shot_mixed_result_sexism <- few_shot_mixed_result_sexism[, c("example_set", "Actual classification", "Not sexist", "Sexist")]
few_shot_mixed_result_sexism_overall <- few_shot_mixed_result_sexism_overall[, c("Actual classification", "Not sexist", "Sexist")] %>% mutate(example_set = "All", .before="Actual classification")

table <- few_shot_mixed_result_sexism %>% 
  # select(!example_set) %>%
  rbind(few_shot_mixed_result_sexism_overall) %>%
  mutate(example_set = case_when(.$`Actual classification` == "Sexist" ~ "", TRUE ~ example_set)) %>%
  rename("Example set" = example_set)

knitr::kable(table,
             caption = "Classification of sexist statements with mixed-category few-shot learning",
             booktabs = TRUE,
             linesep="") %>%
  kableExtra::add_header_above(c(" " = 2, "GPT-3 classification"=2))  %>%
  kableExtra::row_spec(seq(2, 20, by=2), hline_after = TRUE)
  # kableExtra::pack_rows(index=c("Example set 1"=2, 
  #                               "Example set 2"=2, 
  #                               "Example set 3"=2, 
  #                               "Example set 4"=2, 
  #                               "Example set 5"=2, 
  #                               "Example set 6"=2,
  #                               "Example set 7"=2,
  #                               "Example set 8"=2,
  #                               "Example set 9"=2,
  #                               "Example set 10"=2,
  #                               "Overall"=2))
```

```{r fewshotmixed-summary}
few_shot_mixed_result_racism_overall <- few_shot_mixed_result_racism_overall %>% mutate(example_set = 11, .before="Actual classification")
all_results_racism <- rbind(few_shot_mixed_result_racism, few_shot_mixed_result_racism_overall)

few_shot_mixed_result_sexism_overall <- few_shot_mixed_result_sexism_overall %>% mutate(example_set = 11, .before="Actual classification")
all_results_sexism <- rbind(few_shot_mixed_result_sexism, few_shot_mixed_result_sexism_overall)

all_summary <- tibble()
for (i in 1:11){
  example_i_racism <- all_results_racism %>% filter(example_set == i) %>% select(!example_set)

  tp_r <- example_i_racism[2, 3] %>% as.numeric()
  tn_r <- example_i_racism[1, 2] %>% as.numeric()
  fp_r <- example_i_racism[1, 3] %>% as.numeric()
  fn_r <- example_i_racism[2, 2] %>% as.numeric()

  few_shot_summary <- tibble(example_set = rep(i, 4),
                             Category = rep("Racism", 4), 
                             Metric = c("Accuracy", "Precision", "Recall", "F1"), 
                             Percent = few_racism_all) %>%
  pivot_wider(names_from = Metric, values_from = Percent)

  all_summary <- rbind(all_summary, few_shot_summary)

  example_i_sexism <- all_results_sexism %>% filter(example_set == i) %>% select(!example_set)

  tp_s <- example_i_sexism[2, 3] %>% as.numeric()
  tn_s <- example_i_sexism[1, 2] %>% as.numeric()
  fp_s <- example_i_sexism[1, 3] %>% as.numeric()
  fn_s <- example_i_sexism[2, 2] %>% as.numeric()

  few_shot_summary <- tibble(example_set = rep(i, 4),
                             Category = c(rep("Sexism", 4)), 
                             Metric = c("Accuracy", "Precision", "Recall", "F1"), 
                             Percent = c(few_sexism_all))  %>%
  pivot_wider(names_from = Metric, values_from = Percent)

  all_summary <- rbind(all_summary, few_shot_summary)
}

table <- all_summary %>%
  # select(example_set, Metric, Percent) %>% 
  mutate(example_set = as.character(example_set),
         example_set = case_when(example_set == 11 ~ "All", TRUE ~ example_set),
         example_set = case_when(Category == "Sexism" ~ "", TRUE ~ example_set)) %>%
  rename("Example set" = example_set)

knitr::kable(table,
             caption="Performance of mixed-category few-shot learning in racist text classification",
               # col.names=c("", "Percent"),
             booktabs=TRUE,
             linesep = "") %>%
  kableExtra::row_spec(seq(2, 20, by=2), hline_after = TRUE)

# knitr::kable(list(table[1:24, 1:3],
#                   matrix(numeric(), nrow=0, ncol=3),
#                   table[25:44, 1:3]),
#              caption="Performance of mixed-category few-shot learning in racist text classification",
#                # col.names=c("", "Percent"),
#              booktabs=TRUE,
#              linesep = "")
  # kableExtra::pack_rows(index=c("Example set 1"=4,
  #                               "Example set 2"=4,
  #                               "Example set 3"=4,
  #                               "Example set 4"=4,
  #                               "Example set 5"=4,
  #                               "Example set 6"=4,
  #                               "Example set 7"=4,
  #                               "Example set 8"=4,
  #                               "Example set 9"=4,
  #                               "Example set 10"=4,
  #                               "Overall"=4))
```

<!-- ```{r fewshotmixed-summary-sexism} -->
<!-- few_shot_mixed_result_sexism_overall <- few_shot_mixed_result_sexism_overall %>% mutate(example_set = 11, .before="Actual classification") -->
<!-- all_results <- rbind(few_shot_mixed_result_sexism, few_shot_mixed_result_sexism_overall) -->
<!-- all_summary <- tibble() -->
<!-- for (i in 1:11){ -->
<!--   example_i_sexism <- all_results %>% filter(example_set == i) %>% select(!example_set) -->

<!--   tp_s <- example_i_sexism[2, 3] %>% as.numeric() -->
<!--   tn_s <- example_i_sexism[1, 2] %>% as.numeric() -->
<!--   fp_s <- example_i_sexism[1, 3] %>% as.numeric() -->
<!--   fn_s <- example_i_sexism[2, 2] %>% as.numeric() -->

<!--   few_sexism_accuracy <- ((tp_s + tn_s)/(tp_s + tn_s + fp_s + fn_s)) %>% round(4)*100 -->
<!--   few_sexism_precision <- (tp_s/(tp_s + fp_s)) %>% round(4)*100 -->
<!--   few_sexism_recall <- (tp_s/(tp_s + fn_s)) %>% round(4)*100 -->
<!--   few_sexism_f1 <- ((2*few_sexism_precision*few_sexism_recall)/(few_sexism_precision + few_sexism_recall)) %>% round(2) -->
<!--   few_sexism_all <- c(few_sexism_accuracy, few_sexism_precision, few_sexism_recall, few_sexism_f1) -->

<!--   few_shot_summary <- tibble(example_set = rep(i, 4), -->
<!--                              Category = c(rep("Sexism", 4)),  -->
<!--                              Metric = c("Accuracy", "Precision", "Recall", "F1"),  -->
<!--                              Percent = c(few_sexism_all)) -->

<!--   all_summary <- rbind(all_summary, few_shot_summary) -->
<!-- } -->

<!-- table <- all_summary %>% -->
<!--   select(example_set, Metric, Percent) %>%  -->
<!--   mutate(example_set = as.character(example_set), -->
<!--          example_set = case_when(example_set == 11 ~ "All", TRUE ~ example_set), -->
<!--          example_set = case_when(Metric != "Accuracy" ~ "", TRUE ~ example_set)) %>% -->
<!--   rename("Example set" = example_set) -->

<!-- knitr::kable(list(table[1:24, 1:3], -->
<!--                   matrix(numeric(), nrow=0, ncol=3), -->
<!--                   table[25:44, 1:3]), -->
<!--              caption="Performance of mixed-category few-shot learning in sexist text classification", -->
<!--                # col.names=c("", "Percent"), -->
<!--              booktabs=TRUE, -->
<!--              linesep = "") -->
<!--   # kableExtra::pack_rows(index=c("Example set 1"=4, -->
<!--   #                               "Example set 2"=4, -->
<!--   #                               "Example set 3"=4, -->
<!--   #                               "Example set 4"=4, -->
<!--   #                               "Example set 5"=4, -->
<!--   #                               "Example set 6"=4, -->
<!--   #                               "Example set 7"=4, -->
<!--   #                               "Example set 8"=4, -->
<!--   #                               "Example set 9"=4, -->
<!--   #                               "Example set 10"=4, -->
<!--   #                               "Overall"=4)) -->

<!-- ``` -->

@@

<!-- ```{r fewshotmixedinstruct} -->
<!-- few_shot_instruction_result <- -->
<!--   read.csv(here::here( -->
<!--     "outputs/data/few_shot_fixed_examples_instruction_results.csv" -->
<!--   )) -->

<!-- few_shot_instruction_result <- -->
<!--   few_shot_instruction_result %>% -->
<!--   filter(temperature == 0) %>% -->
<!--   select(category, label, answer, example_set) %>% -->
<!--   mutate(example_set = example_set + 1) %>% -->
<!--   mutate(result = ifelse(trimws(label) == trimws(answer), "Match", "Mismatch")) %>% -->
<!--   mutate( -->
<!--     label = case_when( -->
<!--       label == "racist" ~ "Racist", -->
<!--       label == "sexist" ~ "Sexist", -->
<!--       label == "neither" ~ "Neither" -->
<!--     ) -->
<!--   ) %>% -->
<!--   group_by(example_set, result) %>% -->
<!--   summarise(result_cnt = n(), .groups = "drop") %>% -->
<!--   ungroup() %>% -->
<!--   group_by(example_set) %>% -->
<!--   mutate(Percent = result_cnt / sum(result_cnt) * 100, -->
<!--          Percent = round(Percent)) %>% -->

<!--   rename(Result = result, -->
<!--          "Example Set" = example_set, -->
<!--          Count = result_cnt) -->

<!-- knitr::kable( -->
<!--   few_shot_instruction_result, -->
<!--   caption = "Classification of statements with mixed-category few-shot learning, with instruction", -->
<!--   booktabs = TRUE, -->
<!--   linesep = "", -->
<!--   align = 'lllr' -->
<!-- ) -->

<!-- # few_shot_instruction_result %>% -->
<!-- #   group_by(Result) %>% -->
<!-- #   summarise(n = sum(Count)) %>% -->
<!-- #   mutate(Percent = n / sum(n) * 100, -->
<!-- #          Percent = round(Percent)) -->
<!-- ``` -->

```{r fewshotmixedinstruct-racism}
few_shot_instruction_result <-
  read.csv(here::here(
    "outputs/data/few_shot_fixed_examples_instruction_results.csv"
  ))

# Example sets
few_shot_mixed_result_instruct_racism <- 
  few_shot_instruction_result %>%
  mutate(example_set = example_set + 1,
         label = case_when(!grepl("racist", label) ~ "not racist", TRUE ~ "racist"),
         answer = case_when(!grepl("racist", answer) ~ "not racist", TRUE ~ "racist")) %>%
  count(example_set, label, answer) %>%
  pivot_wider(names_from = answer, values_from = n) %>%
  mutate(label = case_when(label == "not racist" ~ "Not racist",
                           label == "racist" ~ "Racist")) %>%
  rename("Actual classification" = label, "Not racist" = "not racist", "Racist" = "racist")

# Overall
few_shot_mixed_result_instruct_racism_overall <- 
  few_shot_instruction_result %>%
  mutate(example_set = example_set + 1,
         label = case_when(!grepl("racist", label) ~ "not racist", TRUE ~ "racist"),
         answer = case_when(!grepl("racist", answer) ~ "not racist", TRUE ~ "racist")) %>%
  count(label, answer) %>%
  pivot_wider(names_from = answer, values_from = n) %>%
  mutate(label = case_when(label == "not racist" ~ "Not racist",
                           label == "racist" ~ "Racist")) %>%
  rename("Actual classification" = label, "Not racist" = "not racist", "Racist" = "racist")

few_shot_mixed_result_instruct_racism <- few_shot_mixed_result_instruct_racism[, c("example_set", "Actual classification", "Not racist", "Racist")]
few_shot_mixed_result_instruct_racism_overall <- few_shot_mixed_result_instruct_racism_overall[, c("Actual classification", "Not racist", "Racist")] %>% mutate(example_set = "All", .before="Actual classification")

table <- few_shot_mixed_result_instruct_racism %>% 
  # select(!example_set) %>%
  rbind(few_shot_mixed_result_instruct_racism_overall) %>%
  mutate(example_set = case_when(.$`Actual classification` == "Racist" ~ "", TRUE ~ example_set)) %>%
  rename("Example set" = example_set)

knitr::kable(table,
             caption = "Classification of racist statements with mixed-category few-shot learning, with instruction",
             booktabs = TRUE,
             linesep="") %>%
  kableExtra::add_header_above(c(" " = 2, "GPT-3 classification"=2)) %>%
  kableExtra::row_spec(seq(2, 20, by=2), hline_after = TRUE)

```{r fewshotmixedinstruct-sexism}
# Example sets
few_shot_mixed_result_instruct_sexism <- 
  few_shot_instruction_result %>%
  mutate(example_set = example_set + 1,
         label = case_when(!grepl("sexist", label) ~ "not sexist", TRUE ~ "sexist"),
         answer = case_when(!grepl("sexist", answer) ~ "not sexist", TRUE ~ "sexist")) %>%
  count(example_set, label, answer) %>%
  pivot_wider(names_from = answer, values_from = n) %>%
  mutate(label = case_when(label == "not sexist" ~ "Not sexist",
                           label == "sexist" ~ "Sexist")) %>%
  rename("Actual classification" = label, "Not sexist" = "not sexist", "Sexist" = "sexist")

# Overall
few_shot_mixed_result_instruct_sexism_overall <- 
  few_shot_instruction_result %>%
  mutate(example_set = example_set + 1,
         label = case_when(!grepl("sexist", label) ~ "not sexist", TRUE ~ "sexist"),
         answer = case_when(!grepl("sexist", answer) ~ "not sexist", TRUE ~ "sexist")) %>%
  count(label, answer) %>%
  pivot_wider(names_from = answer, values_from = n) %>%
  mutate(label = case_when(label == "not sexist" ~ "Not sexist",
                           label == "sexist" ~ "Sexist")) %>%
  rename("Actual classification" = label, "Not sexist" = "not sexist", "Sexist" = "sexist")

few_shot_mixed_result_instruct_sexism <- few_shot_mixed_result_instruct_sexism[, c("example_set", "Actual classification", "Not sexist", "Sexist")]
few_shot_mixed_result_instruct_sexism_overall <- few_shot_mixed_result_instruct_sexism_overall[, c("Actual classification", "Not sexist", "Sexist")] %>% mutate(example_set = "All", .before="Actual classification")

table <- few_shot_mixed_result_instruct_sexism %>% 
  # select(!example_set) %>%
  rbind(few_shot_mixed_result_instruct_sexism_overall) %>%
  mutate(example_set = case_when(.$`Actual classification` == "Sexist" ~ "", TRUE ~ example_set)) %>%
  rename("Example set" = example_set)

knitr::kable(table,
             caption = "Classification of sexist statements with mixed-category few-shot learning, with instruction",
             booktabs = TRUE,
             linesep="") %>%
  kableExtra::add_header_above(c(" " = 2, "GPT-3 classification"=2)) %>%
  kableExtra::row_spec(seq(2, 20, by=2), hline_after = TRUE)

```
```{r fewshotmixedinstruct-summary}
few_shot_mixed_result_instruct_racism_overall <- few_shot_mixed_result_instruct_racism_overall %>% mutate(example_set = 11, .before="Actual classification")
all_results_racism <- rbind(few_shot_mixed_result_instruct_racism, few_shot_mixed_result_instruct_racism_overall)

few_shot_mixed_result_instruct_sexism_overall <- few_shot_mixed_result_instruct_sexism_overall %>% mutate(example_set = 11, .before="Actual classification")
all_results_sexism <- rbind(few_shot_mixed_result_instruct_sexism, few_shot_mixed_result_instruct_sexism_overall)

all_summary <- tibble()
for (i in 1:11){
  example_i_racism <- all_results_racism %>% filter(example_set == i) %>% select(!example_set)

  tp_r <- example_i_racism[2, 3] %>% as.numeric()
  tn_r <- example_i_racism[1, 2] %>% as.numeric()
  fp_r <- example_i_racism[1, 3] %>% as.numeric()
  fn_r <- example_i_racism[2, 2] %>% as.numeric()

  few_shot_summary <- tibble(example_set = rep(i, 4),
                             Category = rep("Racism", 4), 
                             Metric = c("Accuracy", "Precision", "Recall", "F1"), 
                             Percent = few_racism_all) %>%
  pivot_wider(names_from = Metric, values_from = Percent)

  all_summary <- rbind(all_summary, few_shot_summary)

  example_i_sexism <- all_results_sexism %>% filter(example_set == i) %>% select(!example_set)

  tp_s <- example_i_sexism[2, 3] %>% as.numeric()
  tn_s <- example_i_sexism[1, 2] %>% as.numeric()
  fp_s <- example_i_sexism[1, 3] %>% as.numeric()
  fn_s <- example_i_sexism[2, 2] %>% as.numeric()

  few_shot_summary <- tibble(example_set = rep(i, 4),
                             Category = c(rep("Sexism", 4)), 
                             Metric = c("Accuracy", "Precision", "Recall", "F1"), 
                             Percent = c(few_sexism_all)) %>%
  pivot_wider(names_from = Metric, values_from = Percent)

  all_summary <- rbind(all_summary, few_shot_summary)
}

table <- all_summary %>%
  # select(example_set, Metric, Percent) %>% 
  mutate(example_set = as.character(example_set),
         example_set = case_when(example_set == 11 ~ "All", TRUE ~ example_set),
         example_set = case_when(Category == "Sexism" ~ "", TRUE ~ example_set)) %>%
  rename("Example set" = example_set)

knitr::kable(table,
             caption="Performance of mixed-category few-shot learning in racist text classification, with instruction",
               # col.names=c("", "Percent"),
             booktabs=TRUE,
             linesep = "") %>%
  kableExtra::row_spec(seq(2, 20, by=2), hline_after = TRUE)

# knitr::kable(list(table[1:24, 1:3],
#                   matrix(numeric(), nrow=0, ncol=3),
#                   table[25:44, 1:3]),
#              caption="Performance of mixed-category few-shot learning in racist text classification, with instruction",
#                # col.names=c("", "Percent"),
#              booktabs=TRUE,
#              linesep = "")
  # kableExtra::pack_rows(index=c("Example set 1"=4,
  #                               "Example set 2"=4,
  #                               "Example set 3"=4,
  #                               "Example set 4"=4,
  #                               "Example set 5"=4,
  #                               "Example set 6"=4,
  #                               "Example set 7"=4,
  #                               "Example set 8"=4,
  #                               "Example set 9"=4,
  #                               "Example set 10"=4,
  #                               "Overall"=4))
```

<!-- ```{r fewshotmixedinstruct-summary-sexism} -->
<!-- few_shot_mixed_result_instruct_sexism_overall <- few_shot_mixed_result_instruct_sexism_overall %>% mutate(example_set = 11, .before="Actual classification") -->
<!-- all_results <- rbind(few_shot_mixed_result_instruct_sexism, few_shot_mixed_result_instruct_sexism_overall) -->
<!-- all_summary <- tibble() -->
<!-- for (i in 1:11){ -->
<!--   example_i_sexism <- all_results %>% filter(example_set == i) %>% select(!example_set) -->

<!--   tp_s <- example_i_sexism[2, 3] %>% as.numeric() -->
<!--   tn_s <- example_i_sexism[1, 2] %>% as.numeric() -->
<!--   fp_s <- example_i_sexism[1, 3] %>% as.numeric() -->
<!--   fn_s <- example_i_sexism[2, 2] %>% as.numeric() -->

<!--   few_sexism_accuracy <- ((tp_s + tn_s)/(tp_s + tn_s + fp_s + fn_s)) %>% round(4)*100 -->
<!--   few_sexism_precision <- (tp_s/(tp_s + fp_s)) %>% round(4)*100 -->
<!--   few_sexism_recall <- (tp_s/(tp_s + fn_s)) %>% round(4)*100 -->
<!--   few_sexism_f1 <- ((2*few_sexism_precision*few_sexism_recall)/(few_sexism_precision + few_sexism_recall)) %>% round(2) -->
<!--   few_sexism_all <- c(few_sexism_accuracy, few_sexism_precision, few_sexism_recall, few_sexism_f1) -->

<!--   few_shot_summary <- tibble(example_set = rep(i, 4), -->
<!--                              Category = c(rep("Sexism", 4)),  -->
<!--                              Metric = c("Accuracy", "Precision", "Recall", "F1"),  -->
<!--                              Percent = c(few_sexism_all)) -->

<!--   all_summary <- rbind(all_summary, few_shot_summary) -->
<!-- } -->

<!-- table <- all_summary %>% -->
<!--   select(example_set, Metric, Percent) %>%  -->
<!--   mutate(example_set = as.character(example_set), -->
<!--          example_set = case_when(example_set == 11 ~ "All", TRUE ~ example_set), -->
<!--          example_set = case_when(Metric != "Accuracy" ~ "", TRUE ~ example_set)) %>% -->
<!--   rename("Example set" = example_set) -->
